\mytitle

### 2012-03-12 papers/SAS2012/implicitization.tex
hop

Analyzing this loop using widening and narrowing on convex polyhedra
or octagons yields the loop invariant $0 \leq x \leq 51 \land y = x$.
Now, the transition at line~5 becomes feasible; and we analyze the
full loop, starting iterations from $0 \leq x \leq 51 \land y = x$,
and obtain invariant~(\ref{eqn:triangle}) in Fig~\ref{fig:gopan_reps_invariant}.

More generally, this analysis method considers an ascending sequence of subsets of the transitions in the loop body \avirer{(left side of Fig.~\ref{fig:multigraph})};
for each subset, an inductive invariant is computed for the program restricted to it.
The starting subset are the transitions reachable in one step from the loop initialization.
If for a given subset $S$ in the sequence, no transitions outside $S$ are reachable from the inductive invariant attached to $S$, then iterations stop;
otherwise, add these transitions to $S$ and iterate more.
Termination ensues from the finiteness of the control-flow graph.

@@

Guided static analysis, as proposed by \cite{DBLP:conf/sas/GopanR07}, applies to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \ref{sec:path_focusing}, except
that we call the abstract values $X_i^s$ instead of $X_i$ to leave room for
another abstract value $X_i^d$ later.

>>>>

Analyzing this loop using widening and narrowing on convex polyhedra
or octagons yields the loop invariant $0 \leq x \leq 51 \land y = x$.
Now, the transition at line~4 becomes feasible; and we analyze the
full loop, starting iterations from $0 \leq x \leq 51 \land y = x$,
and obtain invariant~(\ref{eqn:triangle}) in Fig~\ref{fig:gopan_reps_invariant}.

More generally, this analysis method considers an ascending sequence of subsets of the transitions in the loop body \avirer{(left side of Fig.~\ref{fig:multigraph})};
for each subset, an inductive invariant is computed for the program restricted to it.
The starting subset consists in the transitions reachable in one step from the loop initialization.
If for a given subset $S$ in the sequence, no transitions outside $S$ are reachable from the inductive invariant attached to $S$, then iterations stop;
otherwise, add these transitions to $S$ and iterate more.
Termination ensues from the finiteness of the control-flow graph.

@@

Guided static analysis, as proposed by \cite{DBLP:conf/sas/GopanR07}, applies to the transition
graph of the program. We now present a new technique applying this analysis on the implicit
multigraph from \cite{Monniaux_Gonnord_SAS11}, thus avoiding control flow merges with
unfeasible paths.
In this section, we use the same notations as \S\ref{sec:path_focusing}, except
that we call the abstract values $X_i^s$ instead of $X_i$ to leave room for
another abstract value $X_i^d$ later.
